Optimal (Multiway) Spatial Joins

### 2024-05-29 msj.tex
yufei

To explain the mapping, consider any tuple $\bm{t} \in \J(R_1',...,R_{k-2}')$. Recall that $B_\bm{t}$ is the intersection of the $k-2$ rectangles $\bm{t}[1], ..., \bm{t}[k-2]$. Let $p$ be the bottom-left corner of $B_\bm{t}$. Define $i$ and $j$ to be values in $[k-2]$ such that $\bm{t}[i] = \gbot(\bm{t})$ and $\bm{t}[j] = \gleft(\bm{t})$; note that the values of $i$ and $j$ can be the same. Point $p$ is the intersection of the bottom edge of $\bm{t}[i]$ and the left edge of $\bm{t}[j]$.

@@

\vgap 
\input{4.2.tex}

>>>>

To explain the mapping, consider any tuple $\bm{t} \in \J(R_1',...,R_{k-2}')$. Recall that $B_\bm{t}$ is the intersection of the $k-2$ rectangles $\bm{t}[1], ..., \bm{t}[k-2]$. Let $p$ be the bottom-left corner of $B_\bm{t}$. Define $i$ and $j$ to be values in $[k-2]$ such that $\bm{t}[i] = \gbot(\bm{t})$ and $\bm{t}[j] = \gleft(\bm{t})$; note that $i$ and $j$ can be the same. Point $p$ is the intersection of the bottom edge of $\bm{t}[i]$ and the left edge of $\bm{t}[j]$.

@@

\noindent \underline{\em Proof of Statement (3).} We first prove that $\dcross_H(\bm{t}) \neq \emptyset$ for any $\bm{t} \in \J(R_1',...,R_{k-2}')$. Set $r' = \gbot(\bm{t})$, and let $r$ be the full rectangle of $r'$. Define $h$ as the lowest segment crossing $r$ (note that $h$ definitely exists because otherwise $r$ has no trimmed rectangle). We will show $h \in \dcross_H(\bm{t})$, and hence $\dcross_H(\bm{t})$ cannot be empty. For this purpose, we need to prove that $h$ crosses both $B_{\bm{t}}$ and $r'$. However, $h$ crossing $r$ implies $h$ crossing $r'$, as has already been argued in our proof of statement (2). It thus remains to show that $h$ crosses $B_\bm{t}$.

By the way $r'$ is defined, the bottom edge of $r'$ must be contained in $h$. Because $r' = \gbot(\bm{t})$, the bottom edge of $B_\bm{t}$ is contained in the bottom edge of $r'$ and hence also contained in $h$. This means that $h \cap B_{\bm{t}}\neq \emptyset$. On the other hand, the x-range of $h$ must contain that of $r'$ (because $h$ crosses $r'$), which in turn must contain that of $B_\bm{t}$ (because $r'$ covers $B_\bm{t}$). Thus, the x-range of $h$ covers that of $B_\bm{t}$. Combining this with $h \cap B_{\bm{t}}\neq \emptyset$ shows that $h$ must cross $B_\bm{t}$.

A symmetric argument shows that $\dcross_V(\bm{t}) \ne \emptyset$ for any $\bm{t} \in \J(R_1',...,R_{k-2}')$.

%In other words, both $\dcross_H(\bm{t})$ and $\dcross_V(\bm{t})$ must have size at least 1.

Next, we will prove 
\myeqn{
    \sum_{\bm{t}\in \J(R_1',...,R_{k-2}')} |\dcross_H(\bm{t})| \cdot |\dcross_V(\bm{t})| \leq \out. \label{eqn:hv:type1:properties:proof-help1}
} 
which implies statement (3) because, for any $\bm{t}$ in the summation, $|\dcross_H(\bm{t})| \ge 1$ and $|\dcross_V(\bm{t})| \ge 1$. Our proof resorts to the algorithm generate-$\J^*$ (see Section~\ref{sec:hv:type1}). This algorithm adds to $\J^*$ exactly as many tuples as calculated by the left hand side of \eqref{eqn:hv:type1:properties:proof-help1}. By statement (2), the $\J^*$ computed must be a subset of $\J(R_1,...,R_{k-2},H,V)$, whose size is $\out$. This establishes the inequality in \eqref{eqn:hv:type1:properties:proof-help1}, which completes the proof of statement (3).
